---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

[![Build Status](https://travis-ci.org/vincenzocoia/powers.svg?branch=master)](https://travis-ci.org/vincenzocoia/powers)

__Note__: This R package is not mean to be "serious". It's just for ~~teaching~~ **learning** purposes. 

## References

This package is based off of Vincenzo's package [powers](https://github.com/vincenzocoia/powers)

## powers

This is an R package that gives `sqrt()` friends by providing other power functions.

## boxcox

This package also allows the easy use of the [box-cox transform](https://en.wikipedia.org/wiki/Power_transform#Box%E2%80%93Cox_transformation). 

## Installation

You can install powers from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("rning-wu/rning-wu-hw07")
```

## Example

See the vignette for more extensive use, but here's an example:

```{r example-reciprocal}
powers::reciprocal(2)
```

And here's an example of the box-cox function: 

```{r example-boxcox}
powers::boxcox(c(1,2,3,4),lambda=10,plot=TRUE)
```


## For Developers

Use the internal `pow` function as the machinery for the front-end functions such as `square`, `cube`, and `reciprocal`. 
